An R Markdown document converted from "GuidelineValidation.ipynb

### 2023-05-10 GuidelineValidation.Rmd
Add files via upload

- `Summary1` contains the mean and standard deviation.
- `Summary2` contains the median and interquartile range.

@@

We then use this table to generate a table containing the estimates of the effect of BMI on every biomarker:

@@

```{r}
save(result_file, file = "result_file.RData")
```

@@

```{r}
rmarkdown::convert_ipynb(, output = xfun::with_ext(input, "Rmd"))
```

>>>>

- `Summary1` contains the mean and standard deviation.
- `Summary2` contains the median and percentiles 2.5, 25, 75 and 97.5.

@@

We then use this table to generate a table containing the estimates of the effect of BMI as well as the covariates on every biomarker:

@@

```{r}
save(result_file, file = "../data/ukb/result_file.RData")
```

@@
